Automated topic naming to support cross-project analysis of software maintenance activities

### 2011-01-22 msr/msr2011.tex
um, yeah. i don't understand rebase i guess.
removed Mens, added Ernst ref
removed F-measure figure, updated supervised figure with random bar.

%XXXXXXXXXXXX OPTIONAL
% Not sure we need this
Mens et al.~\cite{mens08icsm} conducted an empirical study of Eclipse, a popular Java IDE, to verify the claims of Lehman~\cite{lehman97sms}.
% They concerned themselves with source code only, and found Law Seven, ``Declining Quality'', to be too difficult to assess: ``[we lacked an] appropriate measurement of the evolving quality of the system as perceived by the users \cite[p. 388]{mens08icsm}''. 
This paper examines the notions of quality in terms of a consistent ontology, as Mens
et al. call for in their conclusions.

@@

\begin{figure}
  \centering
 \includegraphics[width=0.45\textwidth]{figures/unsupervised-bar-f1}
 \caption{Performance, F1 values (range: 0-1), of unsupervised topic labelling for
   each NFR and per word-list.}
  \label{fig:maxdb-unsup-results-f1}
\end{figure}

@@

% There are several possible applications of \textsf{Nomen}'s techniques. 
% For outside users of the software, \textsf{Nomen} can provide insight into that company's development practices. 
% Are they focused on usability, for example?
% Within the organization \textsf{Nomen} acts as a historical sanity check. 
% Confirmation bias is the difference between what people think happened and what actually happened. 
% Some software releases, for instance, are poorly received since they are quite buggy. 
% \textsf{Nomen} would help explain why this was the case, since it can identify NFRs which are dominating developer attention.

>>>>

%XXXXXXXXXXXX OPTIONAL
% Not sure we need this
%Mens et al.~\cite{mens08icsm} conducted an empirical study of Eclipse, a popular Java IDE, to verify the claims of Lehman~\cite{lehman97sms}.
% They concerned themselves with source code only, and found Law Seven, ``Declining Quality'', to be too difficult to assess: ``[we lacked an] appropriate measurement of the evolving quality of the system as perceived by the users \cite[p. 388]{mens08icsm}''. 
%This paper examines the notions of quality in terms of a consistent ontology, as Menset al. call for in their conclusions.

@@

% \begin{figure}
%   \centering
%  \includegraphics[width=0.45\textwidth]{figures/unsupervised-bar-f1}
%  \caption{Performance, F1 values (range: 0-1), of unsupervised topic labelling for
%    each NFR and per word-list.}
%   \label{fig:maxdb-unsup-results-f1}
% \end{figure}

@@

% There are several possible applications of \textsf{Nomen}'s techniques. 
% For outside users of the software, \textsf{Nomen} can provide insight into that company's development practices. 
% Are they focused on usability, for example?
% Within the organization \textsf{Nomen} acts as a historical sanity check. 
% Confirmation bias is the difference between what people think happened and what actually happened. 
% Some software releases, for instance, are poorly received since they are quite buggy. 
% \textsf{Nomen} would help explain why this was the case, since it can identify NFRs which are dominating developer attention.
\todo[inline]{does this section use supervised learning, and if so what ones?}
